Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-22 Arxiv/main.tex
update computation efficiency

\section{Privacy Analysis}
The differential privacy property of $\hexpmech$ is proved based on the holds of the two properties: \emph{sliding property} and \emph{dilation property}.

@@

\subsection{Computation Efficiency}
\label{subsec_effi}
The formula for computing the local sensitivity presented in Sec. \ref{subsec_emls}:$\max\limits_{\{|x,y'| \leq 1; y'\in \mathcal{X}^n\}}\max\limits_{\{r\in R\}} \{\hellinger(\bysinfer(x), r) - \hellinger(\bysinfer(y'), r)|\}$ can be reduced to $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}\hellinger(\bysinfer(x), \bysinfer(y'))|$ by applying the distance triangle property. i.e., the maximum value over $\max\limits_{r \in R}$ always achieves at $r = \bysinfer(x)$ itself, where $\Delta_{l}u(x) = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(x), \bysinfer(x)) - \hellinger(\bysinfer(y'), \bysinfer(x))|\} = \max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(y'), \bysinfer(x))|\}$. We also have some experiments for validating our proposal as in Fig. \ref{fig_efficiency}, where we calculate the $\max\limits_{\{|x,y'| \leq 1;y'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$. It is shown that maximum value taken when  $r = \bysinfer(x)$.

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{efficiency}
\label{fig_efficiency}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.22\textwidth]{theory_2d.eps}
  \label{subfig_theory_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.22\textwidth]{theory_3d.eps}
  \label{subfig_theory_3d}
  } 
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\centering
    \includegraphics[width=0.48\textwidth]{sampling_2d.eps}
\caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_2d}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
     \includegraphics[width=0.48\textwidth]{sampling_3d.eps}   
\caption{Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_3d}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
     \includegraphics[width=0.48\textwidth]{sampling_4d.eps}    
\caption{Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, Unbalanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_4d}
\end{center}
\end{figure}

In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we consider \emph{balanced} data sets
of observations. This means that in the Beta-Binomial setting the datasets will consist of 50\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d})
the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality and 25\%, 25\%, 25\% and 25\% in 4 dimensionality.
The results show that when the data size increases, the average errors of
$\hexpmech$, Laplace mechanism and decrease. For small datasets,
i.e with size less $300$ in the case of Beta-Binomial models,
both the baseline Laplace mechanisms and improved Laplace mechanism outperform $\hexpmech$.
But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
we considered data sets of the order of 15 thousands elements,
the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved Laplace mechanism.
Similar experimental tendencies were obtained for the Dirichlet-multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).

>>>>

\section{Privacy Proof}
The differential privacy property of $\hexpmech$ is proved based on the holds of the two properties: \emph{sliding property} and \emph{dilation property}.

@@

\subsection{Computation Efficiency Optimization}
\label{subsec_effi}
The formula for computing the local sensitivity presented in Sec. \ref{subsec_baselines}: $LS(\dataobs)=\max\limits_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.$ 
can be reduced to $\max\limits_{\{|\dataobs,\dataobs'| \leq 1; \dataobs'\in \mathcal{X}^n\}}\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs'))|$
by applying the distance triangle property.

Specifically, the maximum value over ${r \in R}$ always achieves at $r = \bysinfer(x)$:
\begin{equation*}
\begin{split}
LS(\dataobs) 
  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs), \bysinfer(\dataobs)) - \hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\} \\
  & = \max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}} \{\hellinger(\bysinfer(\dataobs'), \bysinfer(\dataobs))|\}.
\end{split}
\end{equation*}

This equation is validated by experimental result shown in Fig. \ref{fig_efficiency}. We calculate the $\max\limits_{\{|\dataobs,\dataobs'| \leq 1;\dataobs'\in \mathcal{X}^n\}}$ value for every candidate $r \in R$. It is shown that maximum value taken when  $r = \bysinfer(\dataobs)$.

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{efficiency}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\label{fig_efficiency}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.22\textwidth]{theory_2d.eps}
  \label{subfig_theory_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.22\textwidth]{theory_3d.eps}
  \label{subfig_theory_3d}
  }
\caption{The theory probabilities of candidates in three mechanisms, with balanced data set and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$ }
\label{fig_theory}
\end{center}
\end{figure}
In Fig. \ref{fig_theory} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the theoretical probabilities of outputting the candidates with that distance under the different mechanisms. We consider \emph{balanced} data sets, which means that in the Beta-Binomial model (Figure \ref{subfig_theory_2d}) the datasets will consist of 50\% 1s and the rest 0s, while for the
Dirichelet-Multinomial (Figure  \ref{subfig_theory_3d})
the data will be split in the $k=3$ bins with perecentages of: 33\%, 33\% and 34\% in 3 dimensionality. Same concept in 4 dimensionality.

In Fig. \ref{fig_theory}, candidates of smaller distance from true posterior can be outputted by $\hexpmech$ (in blue line) with larger probability than by baseline Laplace mechanism (in green line). This means $\hexpmech$ can produce good results with larger probability than baseline mechanism. However, the improved Laplace mechanism represented by red line can produce good results with probability higher than $\hexpmech$. It outperforms $\hexpmech$.

@@

\begin{figure}[H]
\begin{center}
\centering
    \includegraphics[width=0.4\textwidth]{sampling_2d.eps}
\caption{Increasing data size with prior $\betad(1,1)$, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_2d}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
     \includegraphics[width=0.4\textwidth]{sampling_3d.eps}   
\caption{Increasing data size with $\dirichlet(1,1,1)$ prior distribution, balanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_3d}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\centering
     \includegraphics[width=0.4\textwidth]{sampling_4d.eps}    
\caption{Increasing data size with $\dirichlet(1,1,1,1)$ prior distribution, Unbalanced datasets and parameters $\epsilon = 1.0$ and $\delta = 10^{-8}$}
\label{fig_vs_datasize_4d}
\end{center}
\end{figure}

In Figures \ref{fig_vs_datasize_2d}, \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d} we still consider \emph{balanced} data sets
of observations. The results show that when the data size increases, the average errors of
$\hexpmech$, Laplace mechanism and decrease. For small datasets,
i.e with size less $300$ in the case of Beta-Binomial models,
both the baseline Laplace mechanisms and improved Laplace mechanism outperform $\hexpmech$.
But for bigger data sets, that is, bigger than $300$, or as in Figure \ref{fig_vs_datasize_2d} where
we considered data sets of the order of 15 thousands elements,
the $\hexpmech$ outperforms the baseline Laplace mechanism, and asymptotically approaches the improved Laplace mechanism.
Similar experimental tendencies were obtained for the Dirichlet-multinomial model (Figure \ref{fig_vs_datasize_3d} and \ref{fig_vs_datasize_4d}).
